---
title: "knapsacklab06-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{knapsacklab06-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(knapsacklab06)
library(parallel) # package used for parallel computation
```

## setup
To install the lab6 package, source it from GitHub with the command `devtools::install_github("........", build_vignettes = TRUE)`.

#### Loading the Test Data

```{r}
RNGversion(min(as.character(getRversion()),"3.5.3"))

set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
)
```

## Usage of the Package

### How the Package works

The package includes three functions to solve the 0-1-knapsack-problem. All of the functions have an input `x` (a dataframe with columns `w` containing the weight of each element and `v` containing the value of the respective element) and `W` (the maximum weight the knapsack can carry).
Furthermore, all the three functions return a list containing the maximum value (or a "good" solution like the `greedy_knapsack` function) under the given weight limit and the elements of this solution.


