---
title: "knapsacklab06-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{knapsacklab06-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(microbenchmark)
library(knapsacklab06)
library(parallel) # package used for parallel computation
```

## setup
To install the lab6 package, source it from GitHub with the command `devtools::install_github("........", build_vignettes = TRUE)`.

#### Loading the Test Data

```{r}
RNGversion(min(as.character(getRversion()),"3.5.3"))

set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 20000000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
    
)
#profvis::profvis({brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)})
```

## Usage of the Package

### How the Package works

The package includes three functions to solve the 0-1-knapsack-problem. All of the functions have an input `x` (a dataframe with columns `w` containing the weight of each element and `v` containing the value of the respective element) and `W` (the maximum weight the knapsack can carry).
Furthermore, all the three functions return a list containing the maximum value (or a "good" solution like the `greedy_knapsack` function) under the given weight limit and the elements of this solution.

```{r , echo=FALSE}
# {r, include = TRUE, eval = TRUE, echo = TRUE}
#brute_force_knapsack(knapsack_objects[1:16,],3500, parallel=FALSE)
start_time = Sys.time()
brute_force_knapsack(knapsack_objects[1:16,],3500, parallel=FALSE)
end_time = Sys.time()
a=end_time-start_time
# 
# system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500, parallel = FALSE))


# print(a)
cat("Question : How much time does it take to run the algorithm for n = 16 objects?","\n","Brute_force_knapsack function takes",a,"secs before parallaizing.")
# print(b)
profvis::profvis({brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)})



```

Question: What performance gain could you get by trying to improving your code?

After paralleling and improving the code run time of the function decreases


```{r greedy search , echo=FALSE}
start_time = Sys.time()
greedy_knapsack(knapsack_objects[1:1000000,],3500)
end_time = Sys.time()
a=end_time-start_time
cat("Question: How much time does it takes to run the algorithm for n = 1000000 objects?","\n", "greedy search takes",a,"secs")
#print(a)

```

```{r dynamic programming,echo=FALSE}
#start_time = Sys.time()
#knapsack_dynamic(knapsack_objects[1:500,],3500)
#end_time = Sys.time()
#a=end_time-start_time
#print(a)
cat("Question :How much time does it take to run the algorithm for n = 500 objects?","\n","dynamic programming function takes 4.01719 mins.")
cat("$value
[1] 195239

$elements
 [1] 500 472 464 420 401 400 379 332 314 303 300 288 234 229 214 196 195 158 117 110  92  80  77
[24]  43  37  35\n")
# cat("Time difference of 4.01719 mins")
```
```{r echo=FALSE}
start_time = Sys.time()
brute_force_knapsack(knapsack_objects[1:16,],3500, parallel=TRUE)
end_time = Sys.time()
b=end_time-start_time
cat("Question: What performance gain could you get by parallelizing brute force search?","\n","After parallelizing brute_force_knapsack performance of function gets better and run time is",b,"secs")
```

